
### Converting Container to Singularity Format Image File

To run on HPC Cluster you must first convert containers to a Singularity Format Image File. 

Once logged into the cluster, the steps include:

Starting an interactive job.

```{bash}

srun -n4 -N1 -p int --pty bash

```

Unsetting a Shell environment variable that would prevent the download of the container

```{bash}

unset HTTPS_PROXY

```

Then saving the container file locally on the cluster.

```{bash}

singularity build /location/inside/cluster/analysis.simg docker://registry.doit.wisc.edu/erwin.lares/analysis

```

Then you have to exit the job.

```{bash}

exit

```

### Generating the submit file 

```{r}
shebang <- c("#!/bin/sh",
             "")

sbatch_options <- c("#SBATCH --partition=shared",
                    "#SBATCH --time=0-04:30:00",
                    "#SBATCH --nodes=1",
                    "#SBATCH --ntasks-per-node=64",
                    "#SBATCH --mem=4000",
                    "#SBATCH --error=job.%J.err",
                    "#SBATCH --output=job.%J.out")

# Make sure to change the above two lines to reflect your appropriate
# file locations for standard error and output

# Now list your executable command (or a string of them).
# Example for code compiled with a software module:

excecutable <- c("MPI_DIR=/software/chtc/easybuild/v2/software/OpenMPI/4.0.5-GCC-9.3.0/",
"mpirun -np 40 singularity exec --bind $MPI_DIR path/to/container.simg Rscript analysis.R")

readr::write_lines(shebang, file = "analysis.sh")
readr::write_lines(sbatch_options, file = "analysis.sh", append = TRUE)
readr::write_lines(excecutable, file = "analysis.sh", append = TRUE)

```


```{r}



```